
\section{Description of the Actual Work}

% used existing gdsms 
These analyses were performed using the Clay \gls{GDSM} developed by the 
\gls{UFD} campaign\cite{clayton_generic_2011}. The Clay \gls{GDSM} is built on the 
GoldSim simulation framework and contaminant transport model. 

This radionuclide transport toolset simulates chemical and physical attenuation 
processes including radionuclide solubility, dispersion phenomena, and 
reversible sorption \cite{golder_goldsim_2010, golder_goldsim_ct_2010}.  
Probabilistic elements of the GoldSim modeling framework enable the models to 
incorporate simple probabilistic \gls{FEPs} that affect repository performance. 

The disposal concept modeled by the Clay \gls{GDSM} includes an optional 
vertical advective fast pathway as well as an \gls{EBS} which 
can undergo rate based dissolution and barrier failure.  Releases from the 
\gls{EBS} enter near field and subsequently far field host rock regions in which 
diffusive and advective transport take place, attenuated by solubility limits as 
well as sorption and dispersion phenomena \cite{clayton_generic_2011}.

\subsection{Mean of the Peak Annual Dose}

In this analysis, repository performance is quantified by radiation dose to a 
hypothetical receptor. Specifically, this sensitivity analysis focuses 
on parameters that affect the mean of the peak annual dose.  The mean of the 
peak annual dose,

\begin{align} \label{MoP}
  D_{MoP,i} &= \frac{\sum_{r=1}^{N}{\max\left[\left.D_{r,i}(t)\right|_{\forall t}\right]}}{N}
  \intertext{where}
  D_{MoP,i} &= \mbox{ mean of peak annual dose due to isotope i } [mrem/yr]\nonumber\\
  D_{r,i}(t) &= \mbox{ year t dose in realization r due to isotope i } [mrem/yr]\nonumber\\
  N &= \mbox{number of realizations, } \nonumber
\end{align}

is a conservative metric of repository performance and should not be confused 
with the peak of the mean annual dose.

%\begin{align} \label{PoM}
%  D_{PoM,i} &= \max\left[{\frac{\sum_{r=1}^{N}{\left.D_{r,i}(t)\right|_{\forall t}}}{N}}\right]\\
%            &= \mbox{peak of the mean annual dose due to isotope i } [mrem/yr].\nonumber
%\end{align}

\subsection{Sampling Scheme}

This analysis has undertaken an analysis strategy to develop a many dimensional 
overview of the key factors in modeled repository performance. To achieve this, 
both individual and dual parametric cases were performed.

Individual parameter cases varied a single parameter of interest in 
detail over a broad range of values. Dual parameter cases were 
performed for pairs of parameters expected to exhibit some covariance. For 
each parameter or pair of parameters, forty simulation 
groups varied the parameter or parameters within the range considered. Each 
case and its parametric range are detailed in Table \ref{tab:Cases}. 

\begin{table}[ht!]
\centering
\footnotesize{
\begin{tabular}{|l|l|l|r|r|}
\multicolumn{5}{c}{\textbf{Simulation Cases}}\\
\hline
\textbf{Case} & \textbf{Parameter} & \textbf{Units} & \textbf{Min. Value} & \textbf{Max. Value}\\
\hline
I     & $D_{eff}$    & $[m^2\cdot s^{-1}]$       & $10^{-8}$    &  $10^{-5}$ \\
      & Inventory              & [MTHM]         & $10^{-4}$    &  $10^1$ \\
\hline
II    & $V_{adv, y}$ & $[m \cdot yr^{-1}]$       & $6.31\times10^{-8}$  &  $6.31\times10^{-4}$ \\
      & $D_{eff}$    & $[m^2\cdot s^{-1}]$       & $10^{-8}$    &  $10^{-5}$ \\
\hline
III   & $S_i$        & $[mol\cdot m^{-3}]$       & $(1\times10^{-9})\langle S_i\rangle $    &  $(5\times10^{10})\langle S_i\rangle $ \\
\hline
IV    & $K_{d,i}$    & $[m^3\cdot kg^{-1}]$       & $(1\times10^{-9})\langle K_{d,i}\rangle $    &  $(5\times10^{10})\langle K_{d,i}\rangle $ \\
\hline
V     & $R_{WFDeg.}$           & $[yr^{-1}]$       & $10^{-9}$    &  $10^{-2}$ \\
      & Inventory              & [MTHM]         & $10^{-4}$    &  $10^1$ \\
\hline 
VI    & $t_{WPFail}$        & $[yr]$         & $10^3$    &  $10^7$ \\
      & $D_{eff}$           & $[m^2\cdot s^{-1}]$       & $10^{-8}$    &  $10^{-5}$ \\
\hline
\end{tabular}
\caption{Each dual and single parameter simulation case had 40 simulation 
groups of 100 realizations each.}
\label{tab:Cases}
}
\end{table}

For each simulation group, a 100 realization simulation was completed. Each
realization held the parameters being analyzed as constant and sampled 
stochastic values for uncertain parameters not being studied.  A sampling scheme 
developed in previous generic disposal media modeling was implemented in this 
model in order to ensure that the each 100 realization simulation sampled 
identical values for uncertain parameters \cite{clayton_generic_2011, 
nutt_generic_2009}.  

